Algorithm explanation

### 2013-09-17 article/interpolation.tex
Minor fix

\paragraph{Farkas's Lemma on linear inequalities}
Let a linear inequality $e_i$ be represented as
$a_{i,1} x_1 + \cdots + a_{i,m} x_m <= a_{i,0}$.  Assuming that
$e_1,\cdots,e_n$ implies $e_0$, there exists
$\lambda_1,\cdots,\lambda_n$ that satisfy
$a_{0,j} = \sum_(i=1)^n \lambda_i * a_{i,j} \quad (j=0, \ldots, m)$.

@@

Let a linear inequality $e_i$ be represented as
$a_{i,1} x_1 + \cdots + a_{i,m} x_m <= a_{i,0}$.  Assuming that
$e_1,\cdots,e_n$ implies $\bot$, there exists
$\lambda_1,\cdots,\lambda_n$ that satisfy
$0 = \sum_(i=1)^n \lambda_i * a_{i,j} \quad (j=1, \ldots, m) \wedge
0 > \sum_(i=1)^n \lambda_i * a_{i,0}$.

@@

\paragraph{Interpolation between conjunctions}
We first present an interpolating algorithm between two conjunctive
sets of linear inequalities $A = \left\lbrace e_1,\ldots,e_m
\right\rbrace$ and $B = \left\lbrace e_{m+1},\ldots,e_{m+n}
\right\rbrace$.  We assume that conjunctions of $A$ and $B$ are
inconsistent.  For later convenience, we call this interpolating
problem $\left( A, B \right)$.  Then there exists an interpolating
linear expression $e_\star$ which satisfies
\begin{align*}
\left\lbrace e_1,\ldots,e_m \right\rbrace & \vdash e_\star \\
e_\star \wedge \left\lbrace e_{m+1},\ldots,e_{m+n} \right\rbrace & \vdash \bot
\end{align*}
For convenience, we assume that any expression $e_i$ have variables
$x_1, \ldots, x_a$.

According to the Farkas's lemma, there exists a set of assignmentqs to
$\lambda_i$, to conclude $\bot$ from a set of linear expressions $A
\cup B$, namely,
\begin{align*}
\exists \lambda_1, \ldots, \lambda_m. \\
a % TODO: coefficient, constant constraints
\end{align*}

>>>>

\paragraph{Farkas's Lemma on linear inequalities}
Let a linear inequality $e_i$ be represented as
$a_{i,1} x_1 + \cdots + a_{i,m} x_m <= a_{i,0}$.  Assuming that
$e_1,\cdots,e_n$ implies $e_0$, there exists
$\lambda_1,\cdots,\lambda_n$ that satisfy
\[a_{0,j} = \sum_{i=1}^n \lambda_i * a_{i,j} \quad (j=0, \ldots,m)\]

@@

Let a linear inequality $e_i$ be represented as
$a_{i,1} x_1 + \cdots + a_{i,m} x_m <= a_{i,0}$.  Assuming that
$e_1,\cdots,e_n$ implies $\bot$, there exists
$\lambda_1,\cdots,\lambda_n$ that satisfy
\[0 = \sum_{i=1}^n \lambda_i a_{i,j} \quad (j=1, \ldots, m) \wedge
0 > \sum_{i=1}^n \lambda_i a_{i,0}\]

@@

\paragraph{Interpolation between conjunctions}
We first present an interpolating algorithm between two conjunctive
sets of linear inequalities $A = \left\lbrace e_1,\ldots,e_m
\right\rbrace$ and $B = \left\lbrace e_{m+1},\ldots,e_{m+n}
\right\rbrace$, where $e_i$ takes a form $\mathbf{a}_i \mathbf{x} + b
\leq 0$.  We assume that conjunctions of $A$ and $B$ are inconsistent.
For later convenience, we call this interpolating problem $\left( A, B
\right)$.  Then there exists an interpolating linear expression
$e_\star$ which satisfies
\begin{align*}
\left\lbrace e_1,\ldots,e_m \right\rbrace & \vdash e_\star \\
e_\star \wedge \left\lbrace e_{m+1},\ldots,e_{m+n} \right\rbrace & \vdash \bot
\end{align*}
For convenience, we assume that any expression $e_i$ have variables
$x_1, \ldots, x_a$.

According to the Farkas's lemma, there exists a set of assignments to
$\lambda_i$ to conclude $\bot$ from a set of linear expressions $A
\cup B$, namely,
\begin{align*}
& \exists \lambda_1, \ldots, \lambda_m. \\
& \sum_{i=1}^{m+n} \lambda_i \mathbf{a}_i = 0\wedge \sum_{i=1}^{m+n} \lambda_i b_i > 0
\end{align*}
